noam_data_exploration_v1

### 2024-06-12 noam_data_exploration_v3.Rmd
test change
last minute changes before June 2024 meeting

str(data)

#pivot long

@@

  geom_path(data = cent, aes(x = NMDS1, y = NMDS2, group = Site_habitat, colour = Site),
            arrow = arrow(length=unit(0.5,"cm"), ends="last", type = "closed"), size = 1) +
  facet_wrap(~Habitat) +
  scale_linetype_manual(values = habitat_linetypes) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        strip.text.x = element_text(size = 25),
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(1.5)), # increase legend text
        legend.title = element_text(size = rel(1.5)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) + # add box around legend
  guides(colour=guide_legend(title.position="top", # make color legend title go above legend
                                     title.hjust =0.5, nrow = 2),
         shape=guide_legend(title.position="top",  # make shape legend title go above legend
                                     title.hjust =0.5,
                            nrow = 2),
         path = guide_legend(title.position="top",  # make shape legend title go above legend
                                     title.hjust =0.5)
         )

@@

```{r beta dispersion, fig.height = 15, fig.width=20}
# Want to plot mean distance to centroid, but not sure how to do that with so many factors/interactions...
# bray_matrix <- vegdist(species_matrix, method = "bray")
# year_beta_disper <- vegan::betadisper(bray_matrix, wide_transect_level_subset$Year)
# year_beta_disper #

@@

(Distance_plot <-
  ggplot(data = beta_disper_means) +
  geom_point(aes(x = Year, y = Distance_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Distance_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Distance_mean - Distance_se , ymax = Distance_mean + Distance_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Habitat)+
  labs(title = "Distance to centroid\n", y = "Distance\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )

@@

# best model based on dredge:
diversity_best <-  glmmTMB(Cover_cv ~ Shannon_mean*Site + Site*Habitat + (1|Site_habitat), family = Gamma(link = "log"), data = diversity_stability)
summary(diversity_best) # very low variance in random effect, which is great
Anova(diversity_best) # Interactions all significant
plot(dp <- simulateResiduals(diversity_best)) # some outliers, but otherwise good model fit. I am fine with this.

(richness_cv_plot = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Richness_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 8) + 
   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

(shannon_cv_plot = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r variance vs mean diversity plot, fig.height = 8, fig.width = 10}
(diversity_mean_cv_plot = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Shannon_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# More diverse regions are also those that fluctuate the least in their diversity

(diversity_mean_cv_plot_2 = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Shannon_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
#  facet_wrap(~Site) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         ) # awesome relationship
```

@@

```{r turnover, fig.height = 30, fig.width=25}
library(codyn)
transect_level$Site_habitat <-  paste(transect_level$Site, transect_level$Habitat)
transect_level$Stratum <- paste(transect_level$Site, "-", transect_level$Habitat, "-", transect_level$Transect)
total_turnover<-
  turnover(
  df = transect_level,
  time.var = "Year",
  species.var = "Taxa",
  abundance.var = "Mean_cover",
  replicate.var = "Stratum",
  metric = "total"
)

@@

(turnover_plot <-
  ggplot(data = turnover_means) +
  geom_point(aes(x = Year, y = Turnover_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Turnover_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Turnover_mean - Turnover_se , ymax = Turnover_mean + Turnover_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site_habitat, nrow = 6)+
  labs(title = "a. Turnover\n", y = "Total turnover\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )
# this is useless

@@

@@

ggplot(rate_change, aes(interval, distance, colour = Site, shape = Habitat, group = Site_habitat, linetype = Habitat)) +
  facet_wrap(~Site) + 
  geom_point() +
  scale_colour_manual(values = site_colours) +
  scale_linetype_manual(values = habitat_linetypes) +
  stat_smooth(method = "lm", se = T, size = 2) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site)+
#  labs(y = "Distance\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
```

>>>>

str(data)
# test
#pivot long

@@

  geom_path(data = cent, aes(x = NMDS1, y = NMDS2, group = Site_habitat, colour = Site),
            arrow = arrow(length=unit(0.5,"cm"), ends="last", type = "closed"), size = 1) +
  facet_wrap(~factor(Habitat, levels=c('Fringing','Backreef','Outer 10','Outer 17'))) +
  scale_linetype_manual(values = habitat_linetypes) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        strip.text.x = element_text(size = 25),
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(1.5)), # increase legend text
        legend.title = element_text(size = rel(1.5)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black")) + # add box around legend
  guides(colour=guide_legend(title.position="top", # make color legend title go above legend
                                     title.hjust =0.5, nrow = 2),
         shape=guide_legend(title.position="top",  # make shape legend title go above legend
                                     title.hjust =0.5,
                            nrow = 2),
         path = guide_legend(title.position="top",  # make shape legend title go above legend
                                     title.hjust =0.5)
         )

@@

```{r beta dispersion, fig.height = 15, fig.width=20}
# Want to plot mean distance to centroid, but not sure how to do that with so many factors/interactions...
 bray_matrix <- vegdist(species_matrix, method = "bray")
# year_beta_disper <- vegan::betadisper(bray_matrix, wide_transect_level_subset$Year)
# year_beta_disper #

@@

(Distance_plot <-
  ggplot(data = beta_disper_means) +
  geom_point(aes(x = Year, y = Distance_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Distance_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Distance_mean - Distance_se , ymax = Distance_mean + Distance_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~factor(Habitat, levels=c('Fringing','Backreef','Outer 10','Outer 17')))+
  labs(title = "Distance to centroid\n", y = "Distance\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )
# beta dispersion increases as we move from forereef to lagoon, lagoon to shore

@@

# best model based on dredge:
diversity_best <-  glmmTMB(Cover_cv ~ Shannon_mean*Site + Site*Habitat + (1|Site_habitat), family = Gamma(link = "log"), data = diversity_stability)
summary(diversity_best) # very low variance in random effect, which is great
Anova(diversity_best) # Interactions all significant
plot(dp <- simulateResiduals(diversity_best)) # some outliers, but otherwise good model fit. I am fine with this. 
r.squaredGLMM(diversity_best) # 0.77, 0.77

(shannon_cv_plot = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 8) + 
   scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
    stat_smooth(aes(x = Shannon_mean, y = Shannon_cv),method = "lm", se = T, size = 2) + 
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

(shannon_cv_plot_2 = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Cover_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

@@

```{r variance vs mean diversity plot, fig.height = 8, fig.width = 10}
(diversity_mean_cv_plot = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Shannon_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site) +

  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )
# More diverse regions are also those that fluctuate the least in their diversity

(diversity_mean_cv_plot_2 = 
  ggplot(data = diversity_stability) +
  geom_point(aes(x = Shannon_mean, y = Shannon_cv, colour = Site, shape = Habitat), size = 8, stroke = 2) + 
   scale_colour_manual(values = site_colours) +
   scale_shape_manual(values = habitat_shapes) +

#  facet_wrap(~Site) +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         ) # awesome relationship
```

@@

```{r turnover, fig.height = 30, fig.width=25}
library(codyn)
transect_level$Site_habitat <-  paste(transect_level$Site, transect_level$Habitat)
transect_level$Stratum <- paste(transect_level$Site, "-", transect_level$Habitat, "-", transect_level$Transect)

# the turnover function calculates turnover as the proportion or species that either appear or disappear between timepoints
total_turnover<-
  turnover(
  df = transect_level,
  time.var = "Year",
  species.var = "Taxa",
  abundance.var = "Mean_cover",
  replicate.var = "Stratum",
  metric = "total"
)

@@

(turnover_plot <-
  ggplot(data = turnover_means) +
  geom_point(aes(x = Year, y = Turnover_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Turnover_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Turnover_mean - Turnover_se , ymax = Turnover_mean + Turnover_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site_habitat, nrow = 6)+
  labs(title = "a. Turnover\n", y = "Total turnover\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )
#

# examine appearance and disappearances independently 
# refers to the proportion of species that appeared or disappeared relative to total species pool between two time points

appearance <-
  turnover(
  df = transect_level,
  time.var = "Year",
  species.var = "Taxa",
  abundance.var = "Mean_cover",
  replicate.var = "Stratum",
  metric = "appearance"
)

appearance<- 
  appearance %>%
    separate(Stratum, into = c("Site", "Habitat", "Transect"), sep = "-")
appearance$Site_habitat <- paste(appearance$Site, appearance$Habitat)
# Add back in stratum column

appearance <- appearance %>%
  mutate(across(everything(), str_trim))

str(appearance) # everything became characters

appearance$appearance <- as.numeric(appearance$appearance)
appearance$Year <- as.factor(appearance$Year)
appearance$Site <- as.factor(appearance$Site)
appearance$Habitat <- as.factor(appearance$Habitat)

appearance_means <-
  appearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Appearance_mean = mean(appearance), 
            Appearance_se = sd(appearance)/sqrt(n()))

(appearance_plot <-
  ggplot(data = appearance_means) +
  geom_point(aes(x = Year, y = Appearance_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Appearance_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Appearance_mean - Appearance_se , ymax = Appearance_mean + Appearance_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site_habitat, nrow = 6)+
  labs(title = "b. Appearances\n", y = "Total turnover\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )
#

disappearance <-
  turnover(
  df = transect_level,
  time.var = "Year",
  species.var = "Taxa",
  abundance.var = "Mean_cover",
  replicate.var = "Stratum",
  metric = "disappearance"
)

disappearance<- 
  disappearance %>%
    separate(Stratum, into = c("Site", "Habitat", "Transect"), sep = "-")
disappearance$Site_habitat <- paste(disappearance$Site, disappearance$Habitat)
# Add back in stratum column

disappearance <- disappearance %>%
  mutate(across(everything(), str_trim))

str(disappearance) # everything became characters

disappearance$disappearance <- as.numeric(disappearance$disappearance)
disappearance$Year <- as.factor(disappearance$Year)
disappearance$Site <- as.factor(disappearance$Site)
disappearance$Habitat <- as.factor(disappearance$Habitat)

disappearance_means <-
  disappearance %>%
  dplyr::group_by(Year, Site, Habitat, Site_habitat) %>%
  summarise(Disappearance_mean = mean(disappearance), 
            Disappearance_se = sd(disappearance)/sqrt(n()))

(disappearance_plot <-
  ggplot(data = disappearance_means) +
  geom_point(aes(x = Year, y = Disappearance_mean, colour = Site, shape = Habitat, group = Site_habitat), size = 8, stroke = 2) +
  geom_line(aes(x = Year, y = Disappearance_mean, colour = Site, group = Site_habitat), size = 1.2) +
  geom_errorbar(aes(x = Year, ymin = Disappearance_mean - Disappearance_se , ymax = Disappearance_mean + Disappearance_se, colour = Site,
                    group = Site_habitat), width = 0.5, size = 1.2) +
  scale_colour_manual(values = site_colours) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site_habitat, nrow = 6)+
  labs(title = "c. Disappearance\n", y = "Total turnover\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        )
    )

@@

# rate change
rate_change_table<-
  rate_change(
  df = transect_level,
  time.var = "Year",
  species.var = "Taxa",
  abundance.var = "Mean_cover",
  replicate.var = "Stratum"
)
# kable(rate_change_table)

@@

ggplot(rate_change, aes(interval, distance, colour = Site, shape = Habitat, group = Site_habitat, linetype = Habitat)) +
  facet_wrap(~Site) + 
  geom_point() +
  scale_colour_manual(values = site_colours) +
  scale_linetype_manual(values = habitat_linetypes) +
  stat_smooth(method = "lm", se = T, size = 2) +
  scale_shape_manual(values = habitat_shapes) +
  facet_wrap(~Site)+
#  labs(y = "Distance\n") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.title = element_text(color = "grey20", size = 32, vjust = 0, face = "plain"),
        axis.line.y = element_line(colour = "black"),
        axis.text.y = element_text(color = "grey20", size = 28, hjust = .5, vjust = .5, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(color = "grey20", size = 28, angle = 90, vjust = 0.5, hjust=1, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 32, hjust = .5, vjust = 0, face = "plain"),
        strip.text.x = element_text(size = 32),
        legend.key.size = unit(2, "cm"), # increase legend size
        legend.text = element_text(size = rel(2)), # increase legend text
        legend.title = element_text(size = rel(2.25)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal',
        legend.box.background = element_rect(colour = "black") # make legend horizontal
        ) # I don't think these are linear relationships so the smoother isn't terriibly helpful
```
